\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{etoolbox}
\usepackage{needspace}
\usepackage{fontawesome5}
\hypersetup{
  colorlinks=true,
  urlcolor=black,
}

\begin{document}

%------------------------------------------------------------------------------
% HEADER
%------------------------------------------------------------------------------
\begin{center}
	{\LARGE \textbf{Jonathan Monsalve}} \\[0.5em]
	Mexico City, Mexico \\
	\faPhone \ +52 56 1184 0899 \hspace{1em}
	\faEnvelope \ \href{mailto:j.jmonsalveg@gmail.com}{j.jmonsalveg@gmail.com}
	\hspace{1em}
	\faLinkedin \ \href{http://linkedin.com/in/jonathan-javier-monsalve}{
		linkedin.com/in/jonathan-javier-monsalve} \hspace{1em}
	\faGithub \ \href{https://github.com/jjmonsalveg}{github.com/jjmonsalveg}
\end{center}

\vspace{0.5em}

%------------------------------------------------------------------------------
% SECTION LINE
%------------------------------------------------------------------------------
\newcommand{\sectionline}{
	\noindent\rule{\linewidth}{0.4pt}\vspace{0.1em}
}

%------------------------------------------------------------------------------
% SUMMARY
%------------------------------------------------------------------------------
\section*{Summary}
\sectionline
Engineering Manager and Systems Engineer with over 10 years of experience in
designing and developing diverse computer systems. Passionate about creativity
and innovation, embracing the philosophy that there is always room for
improvement. In today's fast-paced tech environment, adaptability and quick
iteration are crucial. Strong background in web development and Unix-based
operating systems, with expertise in multidisciplinary teamwork, version
control, project planning, and rigorous quality control. Committed to staying
at the forefront of technology through continuous learning and adoption of
new advancements.

%------------------------------------------------------------------------------
% SKILLS
%------------------------------------------------------------------------------
\section*{Skills}
\sectionline
\vspace{-1em}
\begin{itemize}[leftmargin=0.5cm]
	\item \textbf{Languages:} Ruby, Python, Golang, JavaScript
	\item \textbf{Frameworks:} Ruby on Rails, Django, FastAPI, Flask
	\item \textbf{Testing:} RSpec, Minitest, Pytest, Unittest, Cucumber
	\item \textbf{Cloud \& DevOps:} AWS (Lambda, S3, API Gateway, EventBridge,
	      Kinesis, Kafka, CloudWatch), CDK, CloudFormation, Linux Self-Hosting,
	      Serverless Architectures, CI/CD Pipelines
	\item \textbf{Databases:} MySQL, PostgreSQL, MongoDB, DynamoDB
	\item \textbf{Frontend \& UI:} HTML, CSS, JavaScript, Bootstrap
	\item \textbf{Tools:} Jira, Datadog, Sentry, Snowflake
	\item \textbf{Generative AI:} LangChain, Pinecone, Chroma, ChatGPT models,
	      Copilot
	\item \textbf{Soft Skills:} Leadership, Communication, Team Building,
	      Conflict Resolution, Decision-Making, Strategic Planning, Adaptability
\end{itemize}

%------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%------------------------------------------------------------------------------
\section*{Professional Experience}
\sectionline
\vspace{-1em}

\textbf{Quantum / Camino Financial} \hfill \textit{Oct 2021 -- Aug 2024}\\
\textit{Engineering Manager} \hfill \textit{Mexico City, Mexico \& USA}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Hired and developed an engineering team across the United States and
	      Latin America, fostering a culture of technical rigor and continuous
	      improvement.
	\item Led a system design overhaul, migrating from a monolithic architecture
	      to AWS-based microservices, significantly reducing feature development time (2X).
	\item Implemented Test-Driven Development (TDD), continuous integration, and
	      continuous deployment (CI/CD) practices to improve code quality and delivery.
	\item Built an automated Financial Health Analysis product from the ground up,
	      reducing manual effort by 90\% and scaling to support thousands of
	      applications monthly.
	\item Deployed a digitized bank document extraction system, processing over
	      10,000 documents monthly with 95\% accuracy for reliable financial insights.
	\item Integrated decision models to auto-decision 40\% of applications,
	      reducing underwriter workload and speeding up turnaround time.
	\item Collaborated with digital bank connection partners to enable on-demand
	      cash flow analyses, enhancing operational flexibility.
	\item Reduced cash flow analysis time from 35 minutes to 2 minutes per
	      application, boosting productivity and enabling a 17.5x increase in
	      throughput.
\end{itemize}

\textbf{Covalto} \hfill \textit{Jan 2020 -- Oct 2021}\\
\textit{Back-end Developer} \hfill \textit{Mexico City, Mexico}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Developed tailored credit solutions for restaurants in partnership with
	      Uber Eats during the COVID-19 pandemic, showcasing adaptability.
	\item Contributed to the backend of web-based credit card products,
	      accelerating Covalto’s transition into a full-fledged financial institution.
	\item Progressively took on more responsibilities by demonstrating technical
	      expertise and successfully delivering crucial backend projects.
\end{itemize}

\textbf{RunaHR} \hfill \textit{May 2019 -- Dec 2019}\\
\textit{Back-end Leader} \hfill \textit{Mexico City, Mexico}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Promoted to Back-end Leader, scaling the company to support over 2,000
	      businesses and approximately 5,000 employees.
	\item Created and managed five agile squads to support rapid growth and
	      feature delivery.
\end{itemize}

\textbf{} \hfill \textit{Jun 2018 -- May 2019}\\
\textit{Back-end Developer} \hfill \textit{Mexico City, Mexico}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Joined as an early employee to develop a payroll product, securing
	      over 300 clients in the first year.
	\item Contributed core features for the payroll system, supporting the
	      company’s initial product launch.
	\item Implemented authentication and authorization systems, enhancing
	      application security.
\end{itemize}

\textbf{Cleteci Panamá S.A.} \hfill \textit{Oct 2017 -- May 2018}\\
\textit{Technical Leader} \hfill \textit{Remote}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Led a team to develop a comprehensive platform for travel agents,
	      managing flights, hotels, car rentals, and other vacation services.
	\item Advocated for modern development practices, including cloud computing,
	      containerization, automated testing, and CI/CD pipelines.
	\item Set up continuous deployment pipelines, enabling frequent and reliable
	      software releases.
\end{itemize}

\textbf{GN Marketing Inc.} \hfill \textit{Aug 2015 -- Sep 2017}\\
\textit{Full-stack Developer} \hfill \textit{Remote, USA}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Developed and led a location-based advertising product, delivering
	      notifications based on users’ geographic positions.
	\item Pioneered the use of Docker for continuous integration and deployment,
	      streamlining development workflows.
	\item Managed self-hosted Linux servers and improved system architecture.
\end{itemize}

\textbf{Biosoft C.A.} \hfill \textit{Oct 2014 -- Jul 2015}\\
\textit{Full-stack Developer} \hfill \textit{Mérida, Venezuela}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Developed and maintained web applications focusing on login,
	      authentication, and authorization systems.
	\item Created reusable software components such as dynamic forms, document
	      management tools, and workflows using Petri nets.
	\item Contributed to server management and deployment on Linux self-hosted
	      environments.
\end{itemize}

\textbf{Call \& Call Mercadeo Directo C.A.} \hfill \textit{May 2014 -- Sep 2014}\\
\textit{Full-stack Developer} \hfill \textit{Mérida, Venezuela}\\
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item Built web systems for contact center operators to record call results
	      efficiently.
	\item Developed data analysis and quality control tools, enhancing client
	      reporting for major Venezuelan companies.
	\item Managed servers and ensured high availability of web applications in
	      a Red Hat Linux environment.
\end{itemize}

%------------------------------------------------------------------------------
% EDUCATION
%------------------------------------------------------------------------------
\needspace{5\baselineskip}
\section*{Education}
\sectionline
\textbf{Systems Engineering} \hfill \textit{Universidad de Los Andes}\\
\textit{Nov 2006 -- Apr 2013, Mérida, Venezuela}\\
Thesis: \textit{"Challenge to Complexity: BRAIN-CEMISID version 1.0. Design of
	an Operational Kernel for Constructing a Kernel-Brain in Parallel Programming
	using CUDA."}

%------------------------------------------------------------------------------
% TRAINING AND COURSES
%------------------------------------------------------------------------------
\section*{Training and Courses}
\sectionline
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item \textbf{Mastering the System Design Interview}, Sundog Education by Frank
	      Kane, Udemy, Sept 2024
	\item \textbf{AWS Lambda and the Serverless Framework - Hands On Learning!},
	      Paulo Dichone, Udemy, Mar 2023
	\item \textbf{Build a Backend REST API with Python \& Django - Beginner},
	      Mark Winterbottom, Udemy, Aug 2020
	\item \textbf{High Performance Computing: From Theory to Practice},
	      Ph.D. Juan Guillermo Gonzales, Accelogic, Dec 2014
	\item \textbf{Multicores and Multithreading Architectures}, Francisco Tirado,
	      Sep 2013
	\item \textbf{Parallel Programming with Abstractions}, David Padua, Oct 2013
	\item \textbf{Computer Science 101: Introduction to Computer Science},
	      Sebastian Thrun, Udemy, Apr 2012
\end{itemize}

%------------------------------------------------------------------------------
% UNIVERSITY PROJECTS AND RECOGNITIONS
%------------------------------------------------------------------------------
\section*{University Projects and Recognitions}
\sectionline
\begin{itemize}[leftmargin=0.5cm, topsep=0pt, parsep=0pt, itemsep=2pt]
	\item \textbf{Analog Hydraulic System Emulator:} Designed and implemented an
	      analog prototype in MATLAB to control water levels in a tank.
	\item \textbf{Cultural Dictionary of the Andean Páramo:} Developed a PHP-based
	      web project to document animal species and flora.
	\item \textbf{MASTER FLAT Generator for IRAF:} CUDA-based project for processing
	      and transforming space images.
	\item \textbf{Source Code Converter:} Created a Bison/Flex-based tool to convert
	      C code to Python as part of a compilers course.
	\item \textbf{WireFish Network Analyzer:} Built a TCP/IP traffic analyzer
	      inspired by Wireshark, using C++ and Qt.
	\item \textbf{Cleda-plugin Development:} Created a plugin system for the Cleda
	      Framework with XML, Echo3, Java, and Hibernate; recognized at the
	      university's business fair.
\end{itemize}

\end{document}
